Data Dashboard

### 2020-03-03 analysis/05_market_simulator.Rmd
Fixed values

beta <- as.data.frame(matrix(rep(0), nrow = 13))
beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human Rights", "Refugee Relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

####################################################################################

@@

output$data <- renderTable({
    df()
})

@@

@@

```{r}
renderValueBox({
  ai_exp_util <- 15
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

@@

```{r}
renderValueBox({
  gp_exp_util <- 15
  valueBox(gp_exp_util,
           color = "green")
})
```

@@

```{r}
renderValueBox({
  ox_exp_util <- 15
  valueBox(ox_exp_util,
           color = "teal")
})
```

@@

```{r}
renderValueBox({
  rc_exp_util <- 15
  valueBox(rc_exp_util,
           color = "maroon")
})
```

@@

```{r echo=FALSE}
renderGauge({
  ai_rate <- 15
  gauge(ai_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "#FFC30B"))
})
```

@@

```{r echo=FALSE}
renderGauge({
  gp_rate <- 15
  gauge(gp_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "green"))
})
```

@@

```{r echo=FALSE}
renderGauge({
  ox_rate <- 15
  gauge(ox_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "teal"))
})
```

@@

```{r echo=FALSE}
renderGauge({
  rc_rate <- 15
  gauge(rc_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "maroon"))
})
```

@@

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in financial accountability"))

>>>>

beta <- as.data.frame(matrix(rep(0), nrow = 13))
beta$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

testlevels <- as.data.frame(matrix(0, 12, 1))
testlevels[c(3,4,8),] <- 1
testlevels[11,] <- 22.4
testWeights <- c(.4, .15, .53, .19, .32, .09, .00, .1,.14, .16, -.08, 1.24)
testWeights <- as.data.frame(matrix(testWeights, nrow = 12, ncol = 1))

exp(t(testlevels) %*% as.matrix(testWeights))
####################################################################################

@@

@@

renderTable({
    choice = df()
    t(choice[,3]) %*% as.matrix(intercept_mod[,2])

ai_util <- renderTable({
    choice = df()
    exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2]))

@@

```{r}
renderValueBox({
  choice = df()
  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(gp_exp_util,
           color = "green")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(ox_exp_util,
           color = "teal")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(rc_exp_util,
           color = "maroon")
})
```

@@

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)

  ai_rate <- round(1000 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ai_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "#FFC30B"))
})
```

@@

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)

  gp_rate <- round(1000 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(gp_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "green"))
})
```

@@

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)

  ox_rate <- round(1000 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ox_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "teal"))
})
```

@@

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)

  rc_rate <- round(1000 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(rc_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "maroon"))
})
```

@@

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"))
